A Method for the spectroscopic inference of fundamental stellar parameters

### 2014-05-05 tex/paper.tex
better word wrapping
more word wrapping
blacked otu table

\begin{table}[!htb]
\begin{tabular}{ll}
\hline
\hline
Symbol & Description\\
\hline
\hline
$i$ & index specifying a pixel\\
$\lambda_i$ & wavelength corresponding to a given pixel $i$\\
$\vg$ & fundamental stellar parameters, $T_{\rm eff}, \log(g), \Z, \A$\\
  & that parameterize a synthetic spectrum from the grid\\
$\vpp$ & stellar parameters $v \sin i$, $v_z$, $A_V$, and $R^2/d^2$ that\\
  & are applied during ``post processing'' of the synthetic spectrum\\
$\vstar$ & $\{\vg,\vpp \}$\\
$\finst(\lambda)$ & data spectrum\\
$\fsynth(\lambda)$ & synthetic spectrum\\
$c_0, c_1, \ldots$ & Chebyshev polynomial coefficients for residual flux calibration\\
$\vN$ & the set of nuisance parameters composed of $\{c_0, c_1, \ldots, c_N\}$\\
$\vt$ & the parameters $\{\vg, \vpp, \vN\}$ that completely describe a model spectrum\\
$\fDi$ & data flux for a given pixel, $D(\lambda_i)$\\
$\fD$ & data vector comprised of all $\fDi$, $i = \{0, \ldots, N\}$\\
$\fMi$ & model flux for a given pixel, $M(\lambda_i | \vt)$\\
$\fM$ & model vector comprised of all $\fMi$, $i = \{0, \ldots, N\}$\\
$\sigma_i$ & Poisson noise for a given pixel $i$\\
$R_i$ & residuals $\fDi - \fMi$\\
$\fR$ & residual vector $\fD - \fM$\\
$C$ & covariance matrix\\
$k_{\rm global}$  & global covariance kernel\\
$k_{\rm region}$  & regional covariance kernel\\
\hline
\end{tabular}
\caption{Nomenclature used in this document}
\label{tab:nomenclature}
\end{table}

>>>>

%\begin{table}[!htb]
%\begin{tabular}{ll}
%\hline
%\hline
%Symbol & Description\\
%\hline
%\hline
%$i$ & index specifying a pixel\\
%$\lambda_i$ & wavelength corresponding to a given pixel $i$\\
%$\vg$ & fundamental stellar parameters, $T_{\rm eff}, \log(g), \Z, \A$\\
%  & that parameterize a synthetic spectrum from the grid\\
%$\vpp$ & stellar parameters $v \sin i$, $v_z$, $A_V$, and $R^2/d^2$ that\\
%  & are applied during ``post processing'' of the synthetic spectrum\\
%$\vstar$ & $\{\vg,\vpp \}$\\
%$\finst(\lambda)$ & data spectrum\\
%$\fsynth(\lambda)$ & synthetic spectrum\\
%$c_0, c_1, \ldots$ & Chebyshev polynomial coefficients for residual flux calibration\\
%$\vN$ & the set of nuisance parameters composed of $\{c_0, c_1, \ldots, c_N\}$\\
%$\vt$ & the parameters $\{\vg, \vpp, \vN\}$ that completely describe a model spectrum\\
%$\fDi$ & data flux for a given pixel, $D(\lambda_i)$\\
%$\fD$ & data vector comprised of all $\fDi$, $i = \{0, \ldots, N\}$\\
%$\fMi$ & model flux for a given pixel, $M(\lambda_i | \vt)$\\
%$\fM$ & model vector comprised of all $\fMi$, $i = \{0, \ldots, N\}$\\
%$\sigma_i$ & Poisson noise for a given pixel $i$\\
%$R_i$ & residuals $\fDi - \fMi$\\
%$\fR$ & residual vector $\fD - \fM$\\
%$C$ & covariance matrix\\
%$k_{\rm global}$  & global covariance kernel\\
%$k_{\rm region}$  & regional covariance kernel\\
%\hline
%\end{tabular}
%\caption{Nomenclature used in this document}
%\label{tab:nomenclature}
%\end{table}
